Comments on Blair and Sambanis, 2020, \"Forecasting Civil Wars: Theory and Structure in an Age of 'Big Data' and Machine Learning\", *JCR*

### 2020-06-10 paper.Rmd
double-spacing, in case we need it in future

---
title: "Comments on Blair and Sambanis, 2020, \"Forecasting Civil Wars: Theory and Structure in an Age of 'Big Data' and Machine Learning\", *JCR*"
author: 
 - Andreas Beger^[Predictive Heuristics, adbeger@gmail.com. corresponding author]
 - Richard K. Morgan^[V-Dem, rick.morgan2@gmail.com.]
 - Michael D. Ward^[Predictive Heuristics, Duke University, University of Washington, michael.don.ward@gmail.com]
date: "`r format(Sys.time(), '%d %B %Y')`"
thanks: Cassy L. Dorff and Shahryar Minhas both provided helpful feedback on this project. All the code and several additional analyses can be found at our replication archive at https://github.com/rickmorgan2/Blair-Sambanis-replication.
abstract: We examine the research protocols in Blair and Sambanis (2020).  We find that there are several important mistakes and research decisions that determine their results. Fixing these mistakes results in a reversal of their claim that theory based models of escalation are better at predicting onsets of civil war than other kinds of models.  While their model is not very theoretical, it is outperformed by several of the ad hoc, putatively non-theoretical models they devise and examine.  
output: 
  bookdown::pdf_document2:
    keep_tex: true
    keep_md: true
    toc: false
# spacing: double
bibliography: 
  - "`r user <- Sys.info()[['user']]; if (user=='mdw') '/Users/mdw/Git/whistle/master.bib' else 'references.bib'`"
---

>>>>

---
title: "Comments on Blair and Sambanis, 2020, \"Forecasting Civil Wars: Theory and Structure in an Age of 'Big Data' and Machine Learning\", *JCR*"
author: 
 - Andreas Beger^[Predictive Heuristics, adbeger@gmail.com. corresponding author]
 - Richard K. Morgan^[V-Dem, rick.morgan2@gmail.com.]
 - Michael D. Ward^[Predictive Heuristics, Duke University, University of Washington, michael.don.ward@gmail.com]
date: "`r format(Sys.time(), '%d %B %Y')`"
thanks: Cassy L. Dorff and Shahryar Minhas both provided helpful feedback on this project. All the code and several additional analyses can be found at our replication archive at https://github.com/rickmorgan2/Blair-Sambanis-replication.
abstract: We examine the research protocols in Blair and Sambanis (2020).  We find that there are several important mistakes and research decisions that determine their results. Fixing these mistakes results in a reversal of their claim that theory based models of escalation are better at predicting onsets of civil war than other kinds of models.  While their model is not very theoretical, it is outperformed by several of the ad hoc, putatively non-theoretical models they devise and examine.  
output: 
  bookdown::pdf_document2:
    keep_tex: true
    keep_md: true
    toc: false
#header-includes:
#  - \usepackage{setspace}\doublespacing
bibliography: 
  - "`r user <- Sys.info()[['user']]; if (user=='mdw') '/Users/mdw/Git/whistle/master.bib' else 'references.bib'`"
---
